\resheading{Major Projects and Seminar}
\begin{itemize}
\item \textbf{Certification of Python Programs on the basis of Static Information Flow Analysis} \\
      \emph{(M.Tech Project, under the guidance of Prof. R K Shyamsundar)} \hfill {\emph{[ April 2016 - Ongoing ]}} \\[-0.6cm]
      \begin{itemize}
  \item \textit{Objective:} Generation of security constraints for all possible information flow in a given python program and testing of constraints using Read Write Flow Model.\\[-0.5cm]
 	  	  
  \item \textit{Approach:} \\[-0.5cm]
   \begin{itemize}
 \item Tracking of all information flows throughout python program.
 \item Generation of security constraints for each information flow.
 \item Resolution of constraints with Read Write Flow Model.
 \item Development of a platform to automatize all above steps. \\[-0.5cm]
   \end{itemize}
  \item \textit{Future work:} 
  Complete and precise information flow analysis for all features of python and django framework.\\[-0.5cm]
  	        \end{itemize}
\item \textbf{Virtualization and Power Management in Virtualized Platform} \\
\emph{(M.Tech Seminar, under the guidance of Prof. Varsha Apte)} \hfill {\emph{[ Jan 2015 - April 2015 ]}} \\[-0.6cm]
\begin{itemize}
	\item Surveyed various virtualization technologies and studied comparison among them. \\[-0.5cm]
	\item Discussed the challenges observed in these Virtual platforms. \\[-0.5cm]
	\item Surveyed Power Management techniques on a virtualized platform and optimization for reduction of power consumption. \\[-0.5cm]
	\item Studied and reviewed different approaches to reduce power consumption and comparison of them.
\end{itemize}


\end{itemize}
