\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.3in, bottom=0.1in, left=0.55in, right=0.55in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}
\usepackage{graphicx}
\usepackage{wasysym}
%\usepackage[misc]{ifsym}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{hyperref}
\usepackage{palatino}
%\usepackage[top=0.75in, bottom=0.75in, left=0.75in, right=0.75in]{geometry}
\usepackage{booktabs}
\usepackage{fontawesome}
\selectfont
\raggedright

\pagenumbering{gobble}
\fontfamily{SansSerif}

\usepackage{nth}
\usepackage{graphicx}
\usepackage{tabularx}
% \usepackage{comment}
\usepackage{palatino}
\fontfamily{SansSerif}
\selectfont
\usepackage[inline]{enumitem}
\usepackage{multicol}
\usepackage[T1]{fontenc}
\usepackage[ansinew]{inputenc}
\usepackage[none]{hyphenat}
% \usepackage{helvetica}
% \usepackage{array}
\usepackage{color}
\usepackage{newclude}
\definecolor{mygrey}{gray}{0.75}
\textheight=10in
\raggedbottom
% \raggedright
\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.4cm}
\newcommand{\psep}{-0.5cm}
\renewcommand{\labelitemii}{$\circ$}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.375in}
%\addtolength{\evensidemargin}{-0.375in}
%\addtolength{\textwidth}{1.75in}
%\addtolength{\topmargin}{0.1375in}
%\addtolength{\textheight}{1.75in}
\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.988\textwidth}{\textbf{ \vphantom{p\^{E}} \large #1}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
% \textit{#3} & \\
%--------------------------------------------------------
\begin{document}
\textbf{\large{Abhishek Pratap Singh}}\\
\vspace{.1cm}
\indent \Letter ~ abhi1kush@gmail.com \kern 6pc \hfill \phone ~: +91 7738706577 \\
\faHome ~: \indent Bareilly (U.P., India) - 243001 \hfill DOB:
15 Mar 1991

\vspace{0.1cm}
\smallskip
\resheading{Work Experience}
\vspace{-0.4cm}
\begin{itemize}
\item \textbf{Embibe, Bengaluru} 
\emph{(Designation: Software Development Engineer 1)} \hfill {\emph{[ Nov'19 - Present ]}} \\[-0.6cm]
\begin{itemize}
\item Designed and implemented OCR web micro-service for recognizing hand-writing and text in images, automated image preprocessing for better results.
\item Contributed in restful APIs for converting Exam questions in doc format to json objects in database.
\item Worked on redesigning and implementation of automated test question paper generation.  
\end{itemize}
\end{itemize}

\vspace{-0.25cm}
\vspace{-0.2cm}
\begin{itemize}
\item \textbf{Huawei Technologies India Pvt. Ltd, Bangalore} \\
\emph{(Designation: Technical Project Leader)} \hfill {\emph{[ July'17 - Oct'19 ]}}  \\
\textbf{Distributed Network Attached Storage (NAS).}\\[-0.6cm]
\begin{itemize}
	\item Optimizations for large IO operations on distributed file system.\\[-0.5cm]
	\item Worked on protocol for managing \textbf{distributed cache} to accelerate distributed NAS storage.\\[-0.5cm]
	\item Contributed in development of distributed Read Ahead Cache managment.
\end{itemize}
\textbf{IoT: Internet of Things Network Stacks (lwip, uip).}\\[-0.6cm]
\begin{itemize} 
	\item Linux support for RPL(Routing Protocol for Low Power and Lossy Network).\\[-0.5cm]
	\item RFCs implementation for lwip (light weight ip stack). Implementation of IOCTLs. Bug-fixes and modifications in existing open-source code according to requirements.\\[-0.5cm]
	\item Added RPL support in lwip, APIs for adding static default routes and prefixes, Stateless auto configuration of global addresses. Hop by Hop header creation and processing, functionality of enabling/disabling MAC security for a particular flow(TCP/UDP) etc.\\[-0.5cm]
	\item Unit Testing and functional testing using Python and Scappy, using Castellia framework.\\[-0.5cm]
\end{itemize}
\textbf{Proof of Concept and Research Work.}\\[-0.6cm]
\begin{itemize}  	
	\item Designed and implemented mp4 video preview maker in c++ from scratch. \\[-0.5cm]
	\item eBPF and XDP analysis, presentation and demonstration, application of it in DDOS attack mitigation.\\[-0.5cm] 
	\item Simulation results of Multi-path QUIC. Analysis and Presentation for MPQUIC(Alternative of TCP developed by google).\\[-0.5cm]
\end{itemize}
\end{itemize}

\vspace{-0.25cm}

\resheading{ Projects}
\begin{itemize}
\item \textbf{Authentication using Finger Movement on Android phone Touch Screen (Machine Learning).}\hfill \\[-0.6cm]
\begin{itemize}
	\item Tracked finger movement on android touch screen.\\[-0.6cm]
	\item Used Support Vector Machine (SVM) for classification (recognition of authorized user).\\[-0.6cm]
\end{itemize}
%\vspace{-0.2cm}
\vspace{-0.30cm}


\item \textbf{Simulation Modeling of a Web server} \\
\emph{(Guide: Prof. Varsha Apte)} \hfill \emph{(Mar'15 - Apr'15)} \\[-0.6cm]
\begin{itemize}
\item Built a discrete event simulator for a \textbf{closed queuing} web server application; analyze the performance metrics such as CPU Utilization, Throughput and Response time. \\[-0.5cm]

\end{itemize}
	\item \textbf{Extraction of information about RSS and WSS of a Process in Linux kernel.} \hfill \emph{[ CS401 Kernel Programming ]}\hfill 
\emph{(Guided by Prof. Purushottam Kulkarni Spring 2015)} \\[-0.8cm]
\begin{itemize}
\item Implemented loadable kernel module with logic to find out the size of rss and wss of process by using Paging hierarchy. \\[-0.6cm]
\end{itemize}
\end{itemize}

%\vspace{-0.1cm}

\resheading{Education}

%\vspace{-1ex}
\vspace{-.4cm}
\begin{tabular*}{\textwidth}{ l @{\extracolsep{\fill}} l @{\extracolsep{\fill}} l @{\extracolsep{\fill}} l @{\extracolsep{\fill}} l }
\specialrule{1pt}{1em}{0.15em}
\textbf{Examination} & \textbf{University} & \textbf{Institute} & \textbf{Year} & \textbf{CPI/\%} \\
\specialrule{1pt}{0.05em}{0.12em}

Post Graduation (Computer Science \& Engg.) & IIT Bombay & IIT Bombay & 2016 & 8.6
\\
Graduation (Computer Science \& Engg.) & G.B.T.U. &  MMMEC Gorakhpur & 2013 & 68.9
\\
Intermediate & CBSE & SSMV & 2009 & 79.6\\
Matriculation & CBSE & JNV Shahjahanpur & 2007 & 79.2\\
\hline
\end{tabular*}
\resheading{Technical Skills}
\begin{itemize}
\item \textbf{Programming Languages}: Java, C, C++, Python, GoLang \\[-0.5cm]
\item \textbf{Technologies}: Flask, Redis, Docker, ns3, Bash, Awk, Sed, Makefile, Git, Loadable Kerenel Modules \\[-0.5cm]
\item \textbf{Databases}: Postgresql, Elasticsearch \\[-0.5cm]
\end{itemize}
\end{document}