\resheading{Work Experience: Huawei Technologies India Pvt. Ltd.}
\begin{itemize}
	\item \textbf{Research and Development work.}\\[-0.6cm]
	\begin{itemize}  	
		\item {\bf Proof of Concept work}: Designed and implemented mp4 video preview maker in c++ from scratch. \\[-0.5cm]
		\item Experiments and presentation of TCP Congestion control algorithms (Reno, New Reno, Cubic, BBR).\\[-0.5cm]
		\item Performance analysis of netmap, experiments to get highest possible Packet Per Second Rate.\\[-0.5cm]
		\item eBPF and XDP analysis, presentation and demonstration, application of it in DDOS attack mitigation.\\[-0.5cm] 
		\item Simulation results of Multi-path QUIC. Analysis and Presentation for MPQUIC(Alternative of TCP developed by google).\\[-0.5cm]
	\end{itemize}
	\item \textbf{Development Cycle and Formal Release work.} \\
	\textbf{IoT: Internet of Things Network Stacks (lwip, uip).}\\[-0.6cm]
	\begin{itemize} 
	 \item Linux support for RPL(Routing Protocol for Low Power and Lossy Network).\\[-0.5cm]
	 \item RFCs implementation for lwip (light weight ip stack). Implementation of IOCTLs. Bug-fixes and modifications in existing open-source code according to requirements.\\[-0.5cm]
	 \item Added RPL support in lwip, APIs for adding static default routes and prefixes, Stateless auto configuration of global addresses. Hop by Hop header creation and processing, functionality of enabling/disabling MAC security for a particular flow(TCP/UDP) etc.\\[-0.5cm]
	 \item Unit Testing and functional testing using Python and Scappy.\\[-0.5cm]
	 \item Flow level testing using Castellia framework.\\[-0.5cm]
	 \item Quality related tasks: Static tools and CodeDX (Coverity and fortify) issues resolution and analysis.\\[-0.5cm]
	\end{itemize}
	\textbf{Protocol for Distributed Network Attached Storage (NAS).}\\[-0.6cm]
	\begin{itemize}
	\item Optimizations for large IO operations.
	\item Worked on protocol for \textbf{distributed cache} to accelerate distributed NAS storage.\\[-0.6cm]
	\end{itemize}
\end{itemize}
